---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(tidyverse)
library(carbon14)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  dpi = 300
)
```

# carbon14

The goal of carbon14 is to provide a tidy interface to radiocarbon dating, to promote its inclusion in reproducible manuscripts.

## Installation

You can install carbon14 from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("paleolimbot/carbon14")
```

## Example

Radiocarbon ages from [Long Lake, Nova Scotia, Canada](http://www.facetsjournal.com/doi/10.1139/facets-2017-0004):

```{r, echo = FALSE}
dates <- tribble(
  ~sample_id, ~depth, ~age_14C, ~age_error,
  "LL082011-C2-39", 94, 9148, 49,
  "UOC-0844", 70.5, 8582, 28,
  "LL082011-C2-87", 46, 4396, 55,
  "UOC-0845", 37.5, 575, 18,
  "LL082011-C2-124", 9, 623, 34
)
dates
```

Calibrating dates using `calibrate()`:

```{r}
result <- dates %>%
  calibrate(
    measured_age = age_14C, 
    measured_age_error = age_error,
    name = sample_id
  )
result
```

The result is a tibble, which also has a plot method to examine the results:

```{r plot_long_lake}
plot(result)
```

And a summary of the ages can be generated using `summary()` on the `cal_age` column of the output:

```{r}
summary(result$cal_age)
```
